---
title: "Imputed data Functional data analysis for o2 adjusted by APACHE"
output:
  html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F)
library(tidyverse)
library(boot)
library(parallel)
library(foreach)
library(doParallel)
library(doSNOW)
library(pROC)
library(chron)
library(refund)
library(mgcv)
library(fda)
library(plotly)
library(gratia)
```


```{r}

set.seed(456)

auc_estimation <- function(data = dat_o2_grouped, k = 5, y = 'survival', x = 'fd'){
  
  ind <- sample(nrow(data), nrow(data), replace = F)
  dd <- data[ind,]
  dd_list <- split(dd, c(1:k) )
  auc_vec <- NULL

  for(i in 1:k){
    dd_v <- dd_list[[i]]
    dd_t <- do.call(rbind, dd_list[i])
    fml <- as.formula(paste0(y, '~', x))
    fit_glm1 <- glm(fml, data = dd_t, family = binomial)
    pred <- predict(fit_glm1, newdata = dd_v, type = 'response')
    auc_vec[i] <- tryCatch({
      roc(dd_v$ROSC, pred, levels = c(1, 0), direction = ">")$auc
    }, error = function(x)NA)
  }
  mean(auc_vec, na.rm = T)
}


```



## o2 full data reconstruction

```{r}
seed <- 456
dat_o2 <- read.csv('dat_o2_reduction_10_Apr_2020.csv')
dat_o2$t <- as.POSIXct(dat_o2$Time , format = "%H:%M:%S" , tz = "GMT")
dat_o2 <- na.omit(dat_o2)
```


### CPR duration

```{r}
dat_o2 %>%
  group_by(StudyID) %>%
  summarise(CPR_time = range(t)[2]-  range(t)[1],
            y = mean(y),
            ROSC = mean(ROSC),
            survival = mean(survival) ) -> dat_o2_cprtime
dat_o2_cprtime$CPR_time <- as.numeric(dat_o2_cprtime$CPR_time)
```


### Mean of O2

```{r}
dat_o2 %>%
  group_by(StudyID) %>%
  summarise(mean_o2 = mean(y), ROSC =mean(ROSC)) -> dat_o2_mean
```


### CPR duration above o2 level


```{r}
loop_indx1 <- seq(min(dat_o2$y), max(dat_o2$y), by = 1  )
loop_indx1 <- loop_indx1[-1]

clnum <- detectCores()
cl <- makeCluster(clnum)
registerDoSNOW(cl)
#pb <- txtProgressBar(max = length(loop_indx1), style = 3)
#progress <- function(n) setTxtProgressBar(pb, n)
#opts <- list(progress = progress)

auc_list <- foreach(x=loop_indx1,.packages=c('tidyverse', 'pROC')) %dopar% {
  
  dat_o2$dummy <- ifelse(dat_o2$y < x, yes = 0, no = 1)
  dat_o2 %>%
    group_by(StudyID) %>%
    summarise(perc = sum(dummy)/n(),
              y = mean(y),
              survival = mean(survival),
              ROSC = mean(ROSC) ) -> dat_o2_grouped

  replicate(50,{
  auc_estimation(data = dat_o2_grouped, k = 5, y = 'survival', x = 'perc')
  })

}

#close(pb)
stopCluster(cl)

auc_mean <- NULL
for (i in 1:length(auc_list)) {
  auc_mean[i] <- mean(auc_list[[i]], na.rm = T)
  
}

o2_level <- loop_indx1[which.max(auc_mean)]

```



```{r}
dat_o2$dummy <- ifelse(dat_o2$y < o2_level, yes = 0, no = 1)

dat_o2 %>%
  group_by(StudyID) %>%
  summarise(perc = sum(dummy)/n(),
            y = mean(y),
            ROSC = mean(ROSC),
            ROSC = mean(ROSC) ) -> dat_o2_grouped_durtion_above_o2


```




### Derivatives

```{r}
get_derivatives <- function(data = dat_o2, i = 1, k = 10){
  id <- unique(data$StudyID)[i]
  dati <- data[data$StudyID == id,] ## data need to be changed
  diff <- unique(  as.numeric(chron::times(gsub(" PM", "", dati$Time)))  )[2]- unique(  as.numeric(chron::times(gsub(" PM", "", dati$Time)))  )[1]
  dati$Time2 = 4 *   (as.numeric(chron::times(gsub(" PM", "", dati$Time))) - as.numeric(chron::times(gsub(" PM", "", dati$Time)[dim(dati)[1]]))) / diff
  dati$Time2 <- round(dati$Time2)
  fit_gam_all <- tryCatch(
    {
      gam(as.numeric(y) ~ s(Time2, bs="cs", k=k), method="REML" , data = dati)
    }, error = function(x) NA
  )
  
  if( is.na(fit_gam_all)[1] ){
    print( (paste('patients',i,'cannot fit gam function'))  )
    return(NA)
    next
  }

  obj_fd_gam_all <- fderiv(fit_gam_all)
  fd_gam_all <- as.numeric(obj_fd_gam_all$derivatives$`s(Time2)`$deriv)
  df_fd <- cbind(Time2 = (obj_fd_gam_all$eval), fd = fd_gam_all)
  df_fd$Time2 <- round(df_fd$Time2 - df_fd$Time2 %% 4)
  left_join(dati,  df_fd, by = "Time2")

}


```



```{r}
loop_indx1 <- 1:length(unique(dat_o2$StudyID))
clnum <- detectCores()
cl <- makeCluster(clnum)
registerDoSNOW(cl)
#pb <- txtProgressBar(max = length(loop_indx1), style = 3)
#progress <- function(n) setTxtProgressBar(pb, n)
#opts <- list(progress = progress)

dat_o2_derivatives <- foreach(x=loop_indx1,.packages=c('gratia', 'tidyverse','mgcv','chron'), .combine = rbind ) %dopar% get_derivatives(data = dat_o2, i = x, k = 10)

#close(pb)
stopCluster(cl)

```




```{r}
dat_o2_derivatives %>%
  group_by(StudyID) %>%
  summarise(fd = mean(fd, na.rm = T),
            y = mean(y),
            ROSC = mean(ROSC),
            ROSC = mean(ROSC) ) -> dat_o2_grouped_derivatives

```



### Derivatives tunning points

```{r}
dat_o2_derivatives$turn[dat_o2_derivatives$fd > 0] <- 0
dat_o2_derivatives$turn[dat_o2_derivatives$fd <= 0] <- 1


leadit<-function(x) x!=lead(x, default="what")
```



```{r}
dat_o2_derivatives %>%
  group_by(StudyID) %>%
  summarise(turn = sum(leadit(na.omit(turn))),
            y = mean(y),
            ROSC = mean(ROSC),
            ROSC = mean(ROSC) ) -> dat_o2_grouped_tunning_points
```




```{r}
list( dat_o2_cprtime, dat_o2_mean, dat_o2_grouped_durtion_above_o2, dat_o2_grouped_derivatives, dat_o2_grouped_tunning_points) %>% 
  reduce(full_join, by = "StudyID") %>%
  select(c('StudyID', 'survival', 'ROSC.x', 'mean_o2', 'CPR_time', 'perc','fd', 'turn')) -> dat_o2_grouped


names(dat_o2_grouped)[c(3,6)] <- c('ROSC', paste0('duration_above_', o2_level,'_o2_level'))

```



```{r}
dat_demographic <- read.csv('HgbROSCGCSRhythmAGEA_DATA_LABELS_2019-10-03_1955.csv')
dat_demographic_age <- dat_demographic[,c('Screening.ID.','Pre.arrest.APACHE.II.Score')]
names(dat_demographic_age) <- c('StudyID', 'APACHE')
```

```{r}
dat_o2_grouped_demographic <- right_join(dat_demographic_age, dat_o2_grouped)

```





```{r}

cv_prediction_err <- function(data = dat_o2_grouped_demographic, var_int = 'mean_o2', var_adj = c('APACHE'), y = 'survival', cv.seed = 456){
  dd <- data[,c(y, var_int, var_adj)]
  dd <- na.omit(dd)
  data <- dd
  
  
  loop_var <- sort(unique(dd[,var_int]))
  loop_var <- loop_var[-c(1, length(loop_var))]
  err1 <- NULL

  for (i in 1:length(loop_var) ) {
    dd[,var_int] <- ifelse(data[,var_int] < loop_var[i], yes = 0, no = 1)
    dd[,var_int] <- as.factor(dd[,var_int])
    dd[,var_int]
    glm_formula <- as.formula(paste( y , '~ .' ))
    fit_glm1 <- glm(glm_formula, data = dd, family = binomial)
    set.seed(cv.seed)
    err1[i] <- tryCatch({
      cv.glm(data = dd, glmfit = fit_glm1,K = 10)$delta[1]
    }, error = function(x)NA)
      
  
  }
  return(data.frame(thres = loop_var,err = err1))

}

```


```{r}

auc_estimation <- function(data = dat_o2_grouped_demographic, var_int = 'mean_o2', var_adj = c('APACHE', 'CPR_time'), y = 'survival', k = 5){
  ind <- sample(nrow(data), nrow(data), replace = F)
  data <- data[ind,]
  
  dd <- data[,c(y, var_int, var_adj)]
  dd <- na.omit(dd)
  #data <- dd
  
  dd_list <- split(dd, c(1:k) )
  auc_vec <- NULL
  i = 1
  for(i in 1:k){
    dd_v <- dd_list[[i]]
    dd_t <- do.call(rbind, dd_list[i])
    glm_formula <- as.formula(paste( y , ' ~ .' ))
    fit_glm1 <- glm(glm_formula, data = dd_t, family = binomial)
    pred <- predict(fit_glm1, newdata = dd_v, type = 'response')
    auc_vec[i] <- tryCatch({
      roc(dd_v[,y], pred, levels = c(1, 0), direction = ">")$auc
    }, error = function(x)NA)
  }
  mean(auc_vec, na.rm = T)
}

```

## Analysis I - One variable adjusted by age
 
### CPR duration adjusted by age

```{r}
set.seed(seed)

var_int = 'CPR_time'
var_adj = c('APACHE')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', var_adj) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```






### Mean O2 adjusted by age
 
```{r}
var_int = 'mean_o2'
var_adj = c('APACHE')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', var_adj) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```



```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```




### CPR duration above o2 level adjusted by age
 
```{r}
var_int = names(dat_o2_grouped_demographic)[grep('duration', names(dat_o2_grouped_demographic))]
var_adj = c('APACHE')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', var_adj) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```



### Derivatives adjusted by age
 
```{r}
var_int = 'fd'
var_adj = c('APACHE')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', var_adj) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```






### Number of tunning points adjusted by age
 
```{r}
var_int = 'turn'
var_adj = c('APACHE')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', var_adj) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```



## Analysis II - Two variable adjusted by age

### mean o2 and CPR duration adjusted by age
 
```{r}
var_int = 'mean_o2'
var_adj = c('APACHE', 'CPR_time')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```






### mean o2 and derivatives adjusted by age
 
```{r}
var_int = 'mean_o2'
var_adj = c('APACHE', 'fd')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```






### mean o2 and tunning points adjusted by age
 
```{r}
var_int = 'mean_o2'
var_adj = c('APACHE', 'turn')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```





### CPR duration and derivatives adjusted by age
 
```{r}
var_int = 'CPR_time'
var_adj = c('APACHE', 'fd')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```








### CPR duration and turning points adjusted by age
 
```{r}
var_int = 'CPR_time'
var_adj = c('APACHE', 'turn')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```







### CPR duration above o2 level and derivatives adjusted by age
 
```{r}
var_int = names(dat_o2_grouped_demographic)[grep('duration', names(dat_o2_grouped_demographic))]
var_adj = c('APACHE', 'fd')
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```






### Analysis III - Three variable adjusted by age




### mean o2, CPR duration and derivatives adjusted by age
 
```{r}
var_int = 'mean_o2'
var_adj = c('APACHE', 'fd',names(dat_o2_grouped_demographic)[grep('duration', names(dat_o2_grouped_demographic))])
y = 'survival'
cv_pred_err <- cv_prediction_err(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, cv.seed = 456)
```


```{r}
plot(cv_pred_err$thres,cv_pred_err$err, type = 's', xlab = 'Threshold', ylab = 'Prediction Error', main =  paste0('Predictor = ', var_int, ',  ','Adjust by = ', str_c(var_adj, collapse = ' and ')) )
points(cv_pred_err$thres[which.min(cv_pred_err$err)], min(cv_pred_err$err, na.rm = T), col = 'red', pch = 19)
text(x = 0.5 * ( min(cv_pred_err$thres, na.rm = T) + max(cv_pred_err$thres, na.rm = T) ) , 0.5 * ( min(cv_pred_err$err, na.rm = T) + max(cv_pred_err$err, na.rm = T) ) , paste0('Thres (PE) = ', round( cv_pred_err$thres[which.min(cv_pred_err$err)],2 )   ,'(', round(min(cv_pred_err$err, na.rm = T),4), ')' ) , col = 'red')
```




```{r}
auc_rep_1000 <- replicate(1000,{
  auc_estimation(data = dat_o2_grouped_demographic, var_int = var_int, var_adj = var_adj, y = y, k = 5)
})

```



```{r}
hist(auc_rep_1000, breaks = 15, xlab = 'AUC', main = paste0( 'mean (CI) = ',  round(mean(auc_rep_1000),2) , ' (', round(quantile(auc_rep_1000, 0.025),2),' ,',  round(quantile(auc_rep_1000, 0.975),2), ')' ))
abline(v = mean(auc_rep_1000), col = 'red')
abline(v = quantile(auc_rep_1000, 0.025), col = 'red')
abline(v = quantile(auc_rep_1000, 0.975), col = 'red')
```




















































